Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-09 talk/vmil2012/paper.tex
Move some figures around and add sub sections to the evaluation section

From the mentioned benchmarks we collected different datasets to evaluate the
Frequency, the overhead and overall behaviour of guards.
Figure~\ref{fig:benchmarks} summarizes the total number of operations that were
recorded during tracing for each of the benchmarks and what percentage of these
operations are guards. The number of operations was counted on the unoptimized
and optimized traces. Showing that the overall optimization rate is between
65.80\% and 86.23\% of all operations and that the optimization rate for guards
is similar to the general one, as could be assumed based on
Figure~\ref{fig:guard_percent}. These numbers show that guards are a rather
common operation in the traces, which is a reason the put effort into
optimizing them.
\todo{some pie charts about operation distribution}

\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:benchmarks}
\end{figure*}

\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume Data sizes in KiB}
    \label{fig:resume_data_sizes}
\end{figure}

\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards}
    \label{fig:failing_guards}
\end{figure}

@@

\begin{figure*}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and guard data}
    \label{fig:backend_data}
\end{figure*}

@@

>>>>

From the mentioned benchmarks we collected different datasets to evaluate the
Frequency, the overhead and overall behaviour of guards, the results are
summarized in the remainder of this section.

\subsection{Frequency of Guards}
\label{sub:guard_frequency}
\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:benchmarks}
\end{figure*}
Figure~\ref{fig:benchmarks} summarizes the total number of operations that were
recorded during tracing for each of the benchmarks and what percentage of these
operations are guards. The number of operations was counted on the unoptimized
and optimized traces. Showing that the overall optimization rate is between
65.80\% and 86.23\% of all operations and that the optimization rate for guards
is similar to the general one, as could be assumed based on
Figure~\ref{fig:guard_percent}. These numbers show that guards are a rather
common operation in the traces, which is a reason the put effort into
optimizing them.
\subsection{Overhead of Guards}
\label{sub:guard_overhead}
\begin{figure}
    \include{figures/resume_data_table}
    \caption{Resume Data sizes in KiB}
    \label{fig:resume_data_sizes}
\end{figure}

@@

@@

\begin{figure}
    \include{figures/backend_table}
    \caption{Total size of generated machine code and guard data}
    \label{fig:backend_data}
\end{figure}

\subsection{Guard Failures}
\label{sub:guard_failure}
\begin{figure}
    \include{figures/failing_guards_table}
    \caption{Failing guards}
    \label{fig:failing_guards}
\end{figure}
